For Finitary Induction-Induction, \\ Induction is Enough

### 2020-05-02 paper/paper.tex
stuff

In the previous section, using the notions of signature algebras and
signature morphisms, we defined signatures for IITs and what it means
for a model of ETT to support all IITs. In this section we show that
if a model of ETT supports the theory of IIT signatures, then it
supports all IITs.

@@

First we define the term signature algebra using which we obtain the
constructors $\con$ for any IIT signature. Then we will define another
signature algebra which provides the eliminator. Before doing these,
we illustrate the idea on natural numbers.
\begin{example}\label{eg:nat_con}
  For natural numbers, we will define the constructors $\con$ as the
  following natural number algebra
  $(\mathsf{Nat},\mathsf{zero},\mathsf{suc})$. We write variable names
  instead of de Bruijn indices for readability.
  \begin{alignat*}{5}
    & \mathsf{Nat} && := \Tm^\I\,(\cdot\rhd N:\U\rhd z:\El\,N\rhd s:N\Ra\El\,N)\,(\El\,N) \\
    & \mathsf{zero} && := z \\
    & \mathsf{suc} && := \lambda t. (s\oldapp t)
  \end{alignat*}
  Natural numbers are simply $\I$-terms of type $\El\,N$ in the
  context which is the syntactic signature for natural numbers. In
  this context, the only way to define a term of type $\El\,N$ is to
  use $z$ and $s$, corresponding to the $\mathsf{zero}$ and
  $\mathsf{suc}$ constructors.

  To define the action of the eliminator on a natural number
  $n : \mathsf{Nat}$, let's look at the type of the displayed algebra
  interpretation of the number:
  \[
    {\ll n \rr_\ADS}^\D : (\gamma^D : \ll\cdot\rhd N:\U\rhd z:\El\,N\rhd s:N\Ra\El\,N\rr^\D\,\con) \ra \ll\El\,N\rr^\D\,(\ll n\rr^\A\,\con)
  \]
  This says that for a displayed algebra $(N^D,z^D,s^D)$ over $\con$
  (i.e.\ the motives and methods of the eliminator), we get a witness
  of the predicate $\ll\El\,N\rr^\D = N^D$ at the algebra
  interpretation of $n$. This is not yet good, as we would like to get
  $N^D\,n$ instead of $N^D\,(\ll n\rr^\A\,\con)$ as a result. However,
  interpretation into the term signature algebra will imply that
  $n = \ll n\rr^\A\,\con$.
\end{example}

>>>>

In the previous section, using the notions of signature algebras and
signature morphisms, we defined IIT signatures and what it means for a
model of ETT to support all IITs. In this section we show that if a
model of ETT supports the theory of IIT signatures, then it supports
all IITs.

@@

First we define the term signature algebra using which we obtain the
constructors $\con$ for any IIT signature. Then we will define another
signature algebra which provides the eliminator. Before doing these,
we illustrate the idea of both constructions on natural numbers.
\begin{example}\label{eg:nat_con}
  For natural numbers, we will define the constructors $\con$ as the
  following natural number algebra
  $(\mathsf{Nat},\mathsf{zero},\mathsf{suc})$. We write variable names
  instead of de Bruijn indices for readability.
  \begin{alignat*}{5}
    & \mathsf{Nat} && := \Tm^\I\,(\cdot\rhd N:\U\rhd z:\El\,N\rhd s:N\Ra\El\,N)\,(\El\,N) \\
    & \mathsf{zero} && := z \\
    & \mathsf{suc} && := \lambda t. (s\oldapp t)
  \end{alignat*}
  Natural numbers are simply $\I$-terms of type $\El\,N$ in the
  context which is the syntactic signature for natural numbers. In
  this context, the only way to define a term of type $\El\,N$ is to
  use $z$ and $s$, corresponding to the $\mathsf{zero}$ and
  $\mathsf{suc}$ constructors.

  To define the action of the eliminator on a natural number
  $n : \mathsf{Nat}$, let's look at the type of the displayed algebra
  interpretation of the number:
  \[
    {\ll n \rr_\ADS}^\D : (\gamma^D : \ll\cdot\rhd N:\U\rhd z:\El\,N\rhd s:N\Ra\El\,N\rr^\D\,\con) \ra \ll\El\,N\rr^\D\,(\ll n\rr^\A\,\con)
  \]
  This says that for a displayed algebra $\gamma^D=(N^D,z^D,s^D)$ over
  $\con$ (i.e.\ the motives and methods of the eliminator), we get a
  witness of the predicate $\ll\El\,N\rr^\D = N^D$ at the algebra
  interpretation of $n$. This is not yet good, as we would like to get
  $N^D\,n$ instead of $N^D\,(\ll n\rr^\A\,\con)$ as a result. However,
  interpretation into the term signature algebra will imply that
  $n = \ll n\rr^\A\,\con$.
\end{example}
